\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Formatting of lemma.
Small changes to the last subsubsection of section 5.

The component relation relates components to them self which makes sense as well-formed components should contain no \srccm{} specific constructs.

@@

  If
  \begin{itemize}
  \item $\comp$ is a well-formed component, i.e. $\wdjud{\comp}$
  \item One of the following holds:
    \begin{itemize}
    \item $\dom(\comp.\mscode) \subseteq \ta$ and $\comp$ is a reasonable component
    \item $\dom(\comp.\mscode) \mathrel{\#} \ta$
    \end{itemize}
  \end{itemize}
  Then there exists a $W$ such that

@@

  Also, if
 $\npair{\stpair{\Phi}{\Phi}}\in\lrec[\succeq,\gc](W)$ and
 $i \leq n$
and $\Phi_T \term[i]$,
  then $\Phi_S\sterm{\gc}$.
\end{lemma}
We use these three lemmas to prove Theorem~\ref{thm:full-abstraction}
\begin{proof}[Proof of Theorem~\ref{thm:full-abstraction}]
  The proof of both directions are very similar, so we only show the right direction.
  W.l.o.g.\ it suffices to show one direction of the contextual equivalence, so we assume ${\plug{\trg{\context}}{\src{\comp_1}} \term[]{}}$.
  The proof is sketched in Figure~\ref{fig:fa-proof-sketch}.
  By the statement of Theorem~\ref{thm:full-abstraction}, we may assume that $\comp_1$ and $\comp_2$ are well-formed and reasonable.
  Further, by $\tconeq$ the context $\context$ must be well-formed.
  We prove arrow (1) in the figure by using the mentioned assumption about $\comp_1$ and $\context$ along with Lemma~\ref{lem:ftlr-comps}, \ref{lem:compat-context-plug}, and \ref{lem:adequacy}.
  Now we know that ${\plug{\trg{\context}}{\src{\comp_1}} \sterm[]{\gc}{}}$, so by the assumption that $\comp_1$ and $\comp_2$ are contextually equivalent on \srccm{} we get ${\plug{\trg{\context}}{\src{\comp_2}} \sterm[]{\gc}{}}$ which proves arrow (2) in the figure.
  To prove arrow (3), we again apply Lemma~\ref{lem:ftlr-comps}, \ref{lem:compat-context-plug}, and \ref{lem:adequacy}; but this time, we use that $\comp_2$ is well-formed and reasonable and that $\context$ is well-formed.
\end{proof}

>>>>

The component relation relates components to themselves which makes sense as well-formed components should contain no \srccm{} specific constructs.

@@

  If $\comp$ is a well-formed component, i.e. $\wdjud{\comp}$ and either
    $\dom(\comp.\mscode) \subseteq \ta$ and $\comp$ is a reasonable component; or
    $\dom(\comp.\mscode) \mathrel{\#} \ta$,
  then there exists a $W$ such that

@@

  Also, if
 $\npair{\stpair{\Phi}{\Phi}}\in\lrec[\succeq,\gc](W)$ and
 $i \leq n$
and $\Phi_T \term[i]$,
  then $\Phi_S\sterm{\gc}$.
\end{lemma}
We use these three lemmas to prove Theorem~\ref{thm:full-abstraction}
\begin{proof}[Proof of Theorem~\ref{thm:full-abstraction}]
  The proof of both directions are very similar, so we only show the right direction.
  W.l.o.g.\ it suffices to show one direction of the contextual equivalence, so we assume ${\plug{\trg{\context}}{\src{\comp_1}} \term[]{}}$.
  The proof is sketched in Figure~\ref{fig:fa-proof-sketch}.
  By the statement of Theorem~\ref{thm:full-abstraction}, we may assume that the trusted components $\comp_1$ and $\comp_2$ are well-formed and reasonable.
  Further, by $\tconeq$ we may assume the context $\context$ is well-formed.
  We prove arrow (1) in the figure by using the mentioned assumptions about $\comp_1$ and $\context$ along with Lemma~\ref{lem:ftlr-comps}, \ref{lem:compat-context-plug}, and \ref{lem:adequacy}.
  Now we know that ${\plug{\trg{\context}}{\src{\comp_1}} \sterm[]{\gc}{}}$, so by the assumption that $\comp_1$ and $\comp_2$ are contextually equivalent on \srccm{} we get ${\plug{\trg{\context}}{\src{\comp_2}} \sterm[]{\gc}{}}$, i.e.\ arrow (2) in the figure.
  To prove arrow (3), we again apply Lemma~\ref{lem:ftlr-comps}, \ref{lem:compat-context-plug}, and \ref{lem:adequacy}; but this time, we use the assumption that $\comp_2$ is well-formed and reasonable and that $\context$ is well-formed.
\end{proof}
